\documentclass[11pt,stdletter,dateno]{newlfm}
\usepackage{newcent}
\usepackage{url}
\def\baselinestretch{1.1}

\widowpenalty=1000 \clubpenalty=1000
\newlfmP{headermarginskip=15pt}
\newlfmP{sigsize=35pt}
\newlfmP{dateskipafter=15pt}
\newlfmP{addrfromphone}
\newlfmP{addrfromemail}
\PhrPhone{Phone}
\PhrEmail{Email}

\namefrom{Hyundeok.\ Shin}
\addrfrom{%
    \today\\[10pt]
    Microwave Solution Laboratory\\
    Yonsei University\\
    Seoul, South Korea
} \phonefrom{+821063160624 } \emailfrom{hyundeok.shin@yonsei.ac.kr}

\addrto{%
Fairchild Semiconductor\\
HR and Admin division\\
Bucheon, Gyeeonggi-do, South Korea\\
}

\greetto{To Whom It May Concern,} \closeline{Sincerely,}

\begin{document}
\begin{newlfm}

I am writing to apply for the position of Device Engineer at your
company, which was advertised in the Web site Post on 29 May 2012.

In my graduate work, I have focused on device modeling of MOSFETs
with strain technologies for high performance device using TCAD
simulator by synopsys Ltd,. I have strong knowledge of each
fabrication process and strain engineering including physical
concept. I have gained exceptional skills in developing a close
relationship with co-student who is in department of materials
science while graduate student. Additionally, I have reviewed
state-of-the art MOSFET technologies through the papers and SEMATEC
or IBM symposium periodically.

 I have enclosed my resume to support my application. It shows that I will bring
important skills to the position, including:

  \begin{itemize} \itemsep -2pt  % reduce space between items
   \item Process and device simulation with TCAD simulator focused
   on strain technology.
   \item Strong knowledge of fabrication process \& solid-stat physics \&
   mechanical concepts of semiconductor devices.
   \item Fab experience focused on UHV-CVD and other measurement skills(TEM)
   \item learning communication English from Skype with Filipino
   over 1 years.
    \end{itemize}

I would very much enjoy having the opportunity to talk with you
further to discuss the requirements and expectations of the
position, and how I could use my skills to benefit Fairchild
Semiconductor.

Thank you for considering my application. I look forward to hear from you.
test 
\end{newlfm}
\end{document}
